New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-08-15 experiment.tex
Fixes in experiments

We have shown that are situations when Wu--Lin--Weng's method outperforms even the best Bayes-covariant parametric methods. In this section we thus ponder the question whether some non-Bayes covariant method would be more resilients to change of priors. We consider two facets to this question.

@@

The results, as expected, detect no change between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method. However, there is no consistent difference in spread between radial and Wu--Lin--Weng's coupling method. Spread for the radial method is lower for 3 datasets (letter, mnist, usps datasets), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.

>>>>

We have shown that there are situations when Wu--Lin--Weng's method outperforms all Bayes covariant parametric methods we considered. In this section we thus ponder the question whether some non-Bayes-covariant method would be more resilient to change of priors. We consider two facets to this question.

@@

The results, as expected, detect no spread between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method. However, there is no consistent difference in spread between radial and Wu--Lin--Weng's coupling method. Spread for the radial method is lower for 3 datasets (letter, mnist, usps), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.
